Influence of anomalous perpendicular transport on linear tearing mode dynamics in tokamak plasmas

### 2022-01-27 Research/LinearTearingModeTheory/Version1/Paper1.tex
Latest version

\begin{abstract}
The analysis of a previous paper [A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006)] that maps out all of the
two-fluid response regimes of a  linear tearing layer interacting with an externally generated resonant magnetic perturbation, in a large aspect-ratio tokamak plasma,  is generalized to
take into account realistic levels of perpendicular particle transport. A new response-regime map is obtained that differs substantially, in many
respects, from the old one. The improved analysis is first employed to find all of the two-fluid growth-rate regimes of a non-interacting low-mode-number tearing mode in a large aspect-ratio tokamak plasma. 
The analysis is then used to determine the scaling of the error-field penetration threshold with machine
parameters in large aspect-ratio, ohmically heated, tokamak plasmas . A number of penetration regimes are found in which the threshold scales as $n^{1/2}$, where $n$ is the line-averaged
electron number density. A similar scaling has been reported in some experiments. 
\end{abstract}

@@

\subsection{Fundamental Equations}
The four-field model takes the form:\cite{fw}
\begin{align}
\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\hat{\psi}] +\hat{d}_\beta^{\,2}\,[J,\psi]
+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
\end{align}
Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, 
$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
diffusivity at the resonant surface. 
Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
\begin{equation}
\hat{D}_\perp \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
\end{equation}
where $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, and $\chi_{\perp\,e,i}$ is the anomalous
electron/ion perpendicular energy diffusivity in the vicinity of the resonant surface. 
Note that Cole \& Fitzpatrick (2006) neglects the contribution of $\chi_{\perp\,e,i}$ to the perpendicular particle
diffusivity, $D_\perp$, leading to an anomalously small estimate for $D_\perp$. It is this deficiency that we aim to
correct in the present paper.

@@

\subsection{Derivation of Linear Layer Equations}
In accordance with Eqs.~(\ref{e23})--(\ref{e28}), let us write
\begin{align}\label{e31}
\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e36}
\end{align}
where $\zeta=m\,\theta-n\,\varphi$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
Substituting Eqs.~(\ref{e31})--(\ref{e36}) into Eqs.~(\ref{e16})--(\ref{e21}), 
 and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear equations:
\begin{align}\label{e37}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}\nonumber\\[0.5ex]
&\phantom{=} + S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e40}
\end{align}
Here, 
$\tau_H = L_s/(m\,V_A)$ 
is the  hydromagnetic time, 
$\omega_E =(m/r_s)\,V_E(r_s)$
  the 
 ${\bf E}\times {\bf B}$ frequency, 
$\omega_{\ast\,e} = -[\tau/(1+\tau)](m/r_s)V_\ast(r_s)$
the 
   electron diamagnetic
frequency,
$\omega_{\ast\,i} =[1/(1+\tau)](m/r_s)V_\ast(r_s)$
 the  ion diamagnetic
frequency, 
$S=\tau_R/\tau_H$
 the  Lundquist number, 
$\tau_R = \mu_0\,r_s^{\,2}/\eta_\parallel$
 the
 resistive diffusion time, 
$\tau_\varphi
= r_s^{\,2}/\chi_\varphi$
the  toroidal momentum confinement time, and 
$\tau_\perp = r_s^{\,2}/D_\perp$.
  Furthermore, $P_\varphi = \tau_R/\tau_\varphi$ and $P_\perp = \tau_R/\tau_\perp$ are magnetic Prandtl numbers.

@@

Making use of the identities 
\begin{align}\label{e417a}
\lim_{\epsilon\rightarrow 0}\sum_{p=1,\infty} \frac{\sqrt{\epsilon}\,[J_1(j_{1\,p}\,x)]^{2}}{[J_2(j_{1\,p})]^2\,(1+\epsilon\,j_{1\,p}^2)}
&=\frac{1}{4\,x},\\[0.5ex]
\sum_{p=1,\infty} \frac{[J_0(j_{0\,p}\,x)]^2}{[J_1(j_{0\,p}\,x)]^2\,j_{0\,p}^{\,2}} =\frac{1}{2}\,\ln\!\left(\frac{1}{x}\right),\label{e418a}
\end{align}
Eqs.~(\ref{e108}), (\ref{e109d}), and (\ref{e110d}) yield
\begin{equation}\label{torque}
{\mit\Delta}\omega_E = \frac{1}{4}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\frac{\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)}{1+\tau_s^{\,2}\,(\omega_{s\,0}+{\mit\Delta}\omega_E)^2/(-{\mit\Delta}_s')^2}\left(\frac{w_v}{r_s}\right)^4,
\end{equation}
where
\begin{equation}
\tau_V = \left(\frac{q_s}{\epsilon_s}\right)^2\,(\tau_\theta\,\tau_\varphi)^{1/2} + 2\,\ln\!\left(\frac{a}{r_s}\right)\tau_\varphi.
\end{equation}
Here, we have assumed that $\tau_\theta\ll \tau_\varphi$ (as is invariably the case in tokamak plasmas).

@@

\bibitem{wes1} J.A.~Wesson, R.D.~Gill, M.~Hugon, F.C.~Sch\"{u}ller, J.A.~Snipes, D.J.~Ward, et al., Nucl.\ Fusion {\bf 29}, 641 (1989).

\bibitem{vries} P.C.~de\,Vries, M.F.~Johnson, B.~Alper, P.~Buratti, T.C.~Hender, H.R.~Koslowski, et al., Nucl.\ Fusion {\bf 51}, 053018 (2011).

@@

\bibitem{hender} T.C.~Hender, R.~Fitzpatrick, A.W.~Morris, P.G.~Carolan, R.D.~Durst, T.~Edlington, et  al., Nucl.\ Fusion {\bf 32}, 2091 (1992).

@@

\bibitem{wolf} R.C.~Wolf, W~Biel, M.F.M.~de\,Bock, K.H.~Finken, S.~G\"{u}nter, G.M.D.~Hogeweijet, et al., Nucl.\ Fusion {\bf 45}, 1700 (2005).

@@

\bibitem{menard} J.E.~Menard, R.E.~Bell, D.A.~Gates, S.P.~Gerhardt, J.-K.~Park, S.A.~Sabbagh, et al., Nucl.\ Fusion {\bf 50}, 045008 (2010).

\bibitem{wang1} N.~Wang, B.~Rao, Q.~Hu, Y.~Ding, Z.~Chen1, L.~Gao, et al., Nucl.\ Fusion {\bf 54}, 064014 (2014).

\bibitem{wang2} H.-H.~Wang, Y.-W.~Sun, T.-H.~Shi, Q.~Zang, Y.-Q.~Liu, X.~Yang, et al., Nucl.\ Fusion {\bf 58}, 056024 (2018).

@@

\bibitem{lazzaro} E.~Lazzaro, R.J.~Buttery, T.C.~Hender, P.~Zanca, R.~Fitzpatrick, 
M.~Bigi, et al., Phys.\ Plasmas {\bf 9}, 3906 (2002).

@@

\bibitem{buttery} R.J.~Buttery, M.~De'\,Benedetti, D.A.~Gates, Y.~Gribov, T.C.~Hender, R.J.~La\,Haye, et al., Nucl.\ Fusion {\bf 39}, 1827 (1999).

@@

\newpage 
\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{RegimeI.pdf}}
\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=0.9$. The various regimes are
the diffusive-resisitive (DR), the semi-collisional (SC), the resistive-inertial (RI), the viscous-resistive (VR), the viscous-inertial
(VI), and the inertial (I).}\label{f1}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{RegimeII.pdf}}
\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=1.2$. The various regimes are
the diffusive-resisitive (DR), the semi-collisional (SC), the diffusive-inertial (DI), the viscous-resistive (VR), the viscous-inertial
(VI), and the inertial (I).}\label{f2}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{RegimeIII.pdf}}
\caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space. The various regimes are
the diffusive-resisitive (DR), the semi-collisional (SC),  the viscous-resistive (VR), and the resistive-inertial (RI).}\label{f3}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{Scaling.pdf}}
\caption{Error-field penetration regimes in $\hat{\nu}_\ast$-$\hat{\rho}_\ast$ space. The various regimes are the
viscous-resistive-toroidal (${\rm VR}$-$\varphi$), the viscous-resistive-poloidal (${\rm VR}$-$\theta$), the diffusive-resistive-poloidal (${\rm DR}$-$\theta$), and the  diffusive-resistive-toroidal (${\rm DR}$-$\varphi$). }\label{f6}
\end{figure}

>>>>

\begin{abstract}
The analysis of a previous paper [A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006)] that maps out all of the
two-fluid response regimes of a  linear tearing layer interacting with an externally generated resonant magnetic perturbation, in a large aspect-ratio tokamak plasma,  is generalized to
take into account realistic levels of perpendicular particle transport. A new response-regime map is obtained that differs substantially, in many
respects, from the old one. The improved analysis is first employed to find all of the two-fluid growth-rate regimes of a non-interacting low-mode-number tearing mode in a large aspect-ratio tokamak plasma. 
The analysis is then used to determine the scaling of the error-field penetration threshold with machine
parameters in large aspect-ratio, ohmically heated, tokamak plasmas. A number of penetration regimes are found in which the threshold scales as $n^{1/2}$, where $n$ is the line-averaged
electron number density. A similar scaling has been reported in some experiments. 
\end{abstract}

@@

\subsection{Fundamental Equations}
The four-field model takes the form:\cite{fw}
\begin{align}
\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\psi] +\hat{d}_\beta^{\,2}\,[J,\psi]
+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
\end{align}
Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, 
$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
diffusivity at the resonant surface. 
Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
\begin{equation}
\hat{D}_\perp \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
\end{equation}
where $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, and $\chi_{\perp\,e,i}$ is the (anomalous)
perpendicular electron/ion  energy diffusivity in the vicinity of the resonant surface. 
Note that Cole \& Fitzpatrick (2006) neglects the contribution of $\chi_{\perp\,e,i}$ to the perpendicular particle
diffusivity, $D_\perp$, leading to an anomalously small estimate for $D_\perp$. It is this deficiency that we aim to
correct in the present paper.

@@

\subsection{Derivation of Linear Layer Equations}
In accordance with Eqs.~(\ref{e23})--(\ref{e28}), let us write
\begin{align}\label{e31}
\psi(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e36}
\end{align}
where $\zeta=m\,\theta-n\,\varphi$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
Substituting Eqs.~(\ref{e31})--(\ref{e36}) into Eqs.~(\ref{e16})--(\ref{e21}), 
 and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear equations:
\begin{align}\label{e37}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}\nonumber\\[0.5ex]
&\phantom{=} + S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e40}
\end{align}
Here, 
$\tau_H = L_s/(m\,V_A)$ 
is the  hydromagnetic time, 
$\omega_E =(m/r_s)\,V_E(r_s)$
  the 
 ${\bf E}\times {\bf B}$ frequency, 
$\omega_{\ast\,e} = -[\tau/(1+\tau)](m/r_s)V_\ast(r_s)$
the 
   electron diamagnetic
frequency,
$\omega_{\ast\,i} =[1/(1+\tau)](m/r_s)V_\ast(r_s)$
 the  ion diamagnetic
frequency, 
$S=\tau_R/\tau_H$
 the  Lundquist number, 
$\tau_R = \mu_0\,r_s^{\,2}/\eta_\parallel$
 the
 resistive diffusion time, 
$\tau_\varphi
= r_s^{\,2}/\chi_\varphi$
the  toroidal momentum confinement time, and 
$\tau_\perp = r_s^{\,2}/D_\perp$.
  Furthermore, $P_\varphi = \tau_R/\tau_\varphi$ and $P_\perp = \tau_R/\tau_\perp$ are magnetic Prandtl numbers.

@@

Making use of the identities 
\begin{align}\label{e417a}
\lim_{\epsilon\rightarrow 0}\sum_{p=1,\infty} \frac{\sqrt{\epsilon}\,[J_1(j_{1\,p}\,x)]^{2}}{[J_2(j_{1\,p})]^2\,(1+\epsilon\,j_{1\,p}^2)}
&=\frac{1}{4\,x},\\[0.5ex]
\sum_{p=1,\infty} \frac{[J_0(j_{0\,p}\,x)]^2}{[J_1(j_{0\,p}\,x)]^2\,j_{0\,p}^{\,2}} =\frac{1}{2}\,\ln\!\left(\frac{1}{x}\right),\label{e418a}
\end{align}
Eqs.~(\ref{e108}), (\ref{e109d}), and (\ref{e110d}) yield
\begin{equation}\label{torque}
{\mit\Delta}\omega_E =- \frac{1}{4}\left(\frac{\epsilon_s}{q_s}\right)^2\left(\frac{\tau_V}{\tau_H^{\,2}}\right)\frac{\tau_s\,(\omega_{s\,0}+{\mit\Delta}\omega_E)}{1+\tau_s^{\,2}\,(\omega_{s\,0}+{\mit\Delta}\omega_E)^2/(-{\mit\Delta}_s')^2}\left(\frac{w_v}{r_s}\right)^4,
\end{equation}
where
\begin{equation}
\tau_V = \left(\frac{q_s}{\epsilon_s}\right)^2\,(\tau_\theta\,\tau_\varphi)^{1/2} + 2\,\ln\!\left(\frac{a}{r_s}\right)\tau_\varphi.
\end{equation}
Here, we have assumed that $\tau_\theta\ll \tau_\varphi$ (as is invariably the case in tokamak plasmas).

@@

\bibitem{wes1} J.A.~Wesson, R.D.~Gill, M.~Hugon, F.C.~Sch\"{u}ller, J.A.~Snipes, D.J.~Ward, D.V.~Bartlett, 
D.J.~Campbell, P.A.~Duperrex, A.W.~Edwards, et al., Nucl.\ Fusion {\bf 29}, 641 (1989).

\bibitem{vries} P.C.~de\,Vries, M.F.~Johnson, B.~Alper, P.~Buratti, T.C.~Hender, H.R.~Koslowski, V.~Riccardo, and JET-EFDA Contributors, Nucl.\ Fusion {\bf 51}, 053018 (2011).

@@

\bibitem{hender} T.C.~Hender, R.~Fitzpatrick, A.W.~Morris, P.G.~Carolan, R.D.~Durst, T.~Edlington, J.~Ferreira, 
S.J.~Fielding, P.S.~Haynes, J.~Hugill, et al., Nucl.\ Fusion {\bf 32}, 2091 (1992).

@@

\bibitem{wolf} R.C.~Wolf, W~Biel, M.F.M.~de\,Bock, K.H.~Finken, S.~G\"{u}nter, G.M.D.~Hogeweijet,  S.~Jachmich, M.W.~Jakubowski, R.J.E.~Jaspers, A.~Kr\"{a}mer-Flecken, et al., Nucl.\ Fusion {\bf 45}, 1700 (2005).

@@

\bibitem{menard} J.E.~Menard, R.E.~Bell, D.A.~Gates, S.P.~Gerhardt, J.-K.~Park, S.A.~Sabbagh, J.W.~Berkery,
A.~Egan, J.~Kallman, S.M.~Kaye, et al., Nucl.\ Fusion {\bf 50}, 045008 (2010).

\bibitem{wang1} N.~Wang, B.~Rao, Q.~Hu, Y.~Ding, Z.~Chen, L.~Gao, W.~Jin, B.~Yi, W.~Zeng, Q.~Li, et al., Nucl.\ Fusion {\bf 54}, 064014 (2014).

\bibitem{wang2} H.-H.~Wang, Y.-W.~Sun, T.-H.~Shi, Q.~Zang, Y.-Q.~Liu, X.~Yang, 
S.~Gu, K.-Y.~He, X.~Gu, J.-P.~Qian, et al., Nucl.\ Fusion {\bf 58}, 056024 (2018).

@@

\bibitem{lazzaro} E.~Lazzaro, R.J.~Buttery, T.C.~Hender, P.~Zanca, R.~Fitzpatrick, 
M.~Bigi, T.~Bolzonella, R.~Coelho, M.~DeBenedetti S.~Nowak, et al., Phys.\ Plasmas {\bf 9}, 3906 (2002).

@@

\bibitem{buttery} R.J.~Buttery, M.~De'\,Benedetti, D.A.~Gates, Y.~Gribov, T.C.~Hender, R.J.~La\,Haye, P.~Leahy, 
J.A.~Leuer, A.W.~Morris, A.~Santagiustina, et al., Nucl.\ Fusion {\bf 39}, 1827 (1999).

@@

\newpage 
\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{Figure1.pdf}}
\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=0.9$. The various regimes are
the diffusive-resisitive (DR), the semi-collisional (SC), the resistive-inertial (RI), the viscous-resistive (VR), the viscous-inertial
(VI), and the inertial (I).}\label{f1}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{Figure2.pdf}}
\caption{Linear resonant plasma response regimes in $Q$-$P$ space for the case $D=1.2$. The various regimes are
the diffusive-resisitive (DR), the semi-collisional (SC), the diffusive-inertial (DI), the viscous-resistive (VR), the viscous-inertial
(VI), and the inertial (I).}\label{f2}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{Figure3.pdf}}
\caption{Linear tearing mode growth-rate regimes  in $Q_\ast$-$P$ space. The various regimes are
the diffusive-resisitive (DR), the semi-collisional (SC),  the viscous-resistive (VR), and the resistive-inertial (RI).}\label{f3}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.95\textwidth]{Figure4.pdf}}
\caption{Error-field penetration regimes in $\hat{\nu}_\ast$-$\hat{\rho}_\ast$ space. The various regimes are the
viscous-resistive-toroidal (${\rm VR}$-$\varphi$), the viscous-resistive-poloidal (${\rm VR}$-$\theta$), the diffusive-resistive-poloidal (${\rm DR}$-$\theta$), and the  diffusive-resistive-toroidal (${\rm DR}$-$\varphi$). }\label{f6}
\end{figure}
